\section*{Steps}

From the many possibilities, the Independent Study project will start by experimenting with a visualization tool and generating visual representations or animations. As stated previously this is an important contribution, but this is also a vital point for the project to be considered a class for the IGM department. Around half of the academic semester will be allocated to studying and developing this area.

Hopefully such a tool already exists and it is a matter of finding it. In that case more time can be allocated to implementing Builder and Painter strategies. The second part of the semester will be used to study the current status and developments of the field.

At this time it is hard to gather all the information on this topic. It is still only found on papers and there is not a place that gathers and lists the information in a concise manner with a more standardized language, like a book or a chapter in one. A very important part of this study will be to write a report with the current status of Online Ramsey Games played on planar graphs.

Finally, nearing the end of the semester, work will be done towards a final report. The report will discuss the results of the work done during the semester. It will explain the difficulties faced and possible adaptations made to the schedule.

Based on the text found at the proposal form, this study has a total dedication time of at least 135 hours. The table below details how these 135h willbe split among the proposed activities. 

\vspace{0.5cm}
\begin{figure}[!ht]
	\begin{tabular}{|c|c|>{\centering}m{11cm}|@{}m{0pt}@{}}
		\hline
		Weeks & Min. Hours & Activities & \tabularnewline[12pt]
		\hline
		1 & 9 & \begin{itemize}
			\item Find and test visualizations tools for planar graphs
			\item \textbf{*}Decide what tool to use and if a new one is necessary\footnotemark
			
		\end{itemize} & \tabularnewline
		\hline
		2 - 6 & 50 & \begin{itemize}
			\item Develop a program that simulates a builder-painter game for planar graphs. It draws the planar embedding of the graphs generated during play.
		\end{itemize} & \tabularnewline
		\hline
		7 - 8 & 20 & \begin{itemize}
			\item Use a visualization tool to generate a proof that every forest in unavoidable in the class of forests
			\item Show that if all trees with $n$ vertices are unavoidable, then so are all trees with $n+1$ vertices
			\item This would be done by following the inductive proof provided on Online Ramsey Theory \cite{1}
		\end{itemize} & \tabularnewline	
		\hline
		9 - 12 & 41 & \begin{itemize}
			\item Gather all papers that discuss Online Ramsey Games played on Planar Graphs
			\item Write a report that tells the status and the important milestones in this area of study
		\end{itemize} & \tabularnewline
		\hline
		13 - 14 & 15 & \begin{itemize}
			\item Write a report of the work done during the semester
			\item Outline main challenges faced both during the implementation of the proof visualization and the writing of the report
		\end{itemize} & \tabularnewline
		\hline
	\end{tabular}

	\vspace{0.5cm}
	\textbf{*} If a new tool is not necessary: the activities for weeks 2 - 6 become animating other proofs (like the 7-8 week period). 
\end{figure}


\vspace{0.5cm}
\footnotetext{One using \text{https://www.boost.org/doc/libs/1\_49\_0/libs/graph/doc/boyer\_myrvold.html}, maybe}